\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-14 draft.tex
move NSF text between sec:house and sec:est
add NSF references to draft

@@

\item Becker, G., (1983) ``A Theory of Competition among Interest Groups for Political Influence.'' {\em Quarterly Journal of Economics} 98, 371-400.

@@

>>>>

The model is based on that of Banks (2000)

@@

\item Banks, J. S., (2000), ``Buying Supermajorities in Finite Legislatures.'' {\em The American Political Science Review} 94, 677-681.

\item Becker, G., (1983), ``A Theory of Competition among Interest Groups for Political Influence.'' {\em Quarterly Journal of Economics} 98, 371-400.

@@

\item Bafumi, J., Gelman, A., Park., D, Kaplan, N., 2005. Practical Issues in Implementing and Understanding Bayesian Ideal Point Estimation. Political Analysis 13, 171-187.

	\item Buzard, K., 2014a. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.

	\item Buzard, K., 2014b. Self-enforcing Trade Agreements, Dispute Settlement and Separation of Powers. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/2014/04/Self-enforcing-Trade_Agreements.pdf}.

\begin{sloppypar}	
	\item Buzard, K., 2014c. Trade Agreements in the Shadow of Lobbying. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/TradeAgreements_Shadow_Lobbying.pdf}.
		\end{sloppypar}

	\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.

	\item Conconi, P., Facchini, G., Steinhardt, M. F., Zanardi, M., 2012. The political economy of trade and migration: Evidence from the US Congress. HWWI Research Paper 136. Available at: \url{http://hdl.handle.net/10419/67944}.

	\item Dixit, A., Grossman, G., Helpman, E., 1997. Common Agency and Coordination: General Theory and Application to Government Policy Making. Journal of Political Economy 105, 752-769.

	\item Feenstra, R., 1992. How Costly is Protectionism? Journal of Economic Perspectives 6, 159-178.

	\item Gawande, K., Bandyopadhyay, U., 2000. Is Protection for Sale? Evidence on the Grossman-Helpman Theory of Endogenous Protection. The Review of Economics and Statistics 82, 139-152.

	\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.

	\item Gawande, K., Krishna, P., Olarreaga, M., 2012. Lobbying Competition over Trade Policy. International Economic Review 53, 115-132.

	\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.

	\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.

	\item Iaryczower, M., Katz, G., Saiegh, S., 2013. Voting in the Bicameral Congress: Large Majorities as a Signal of Quality. Forthcoming in Journal of Law, Economics, and Organization.

  \item Iida, K., 1996. Involuntary Defection in Two-Level Games. Public Choice 89, 283-303.

	\item Lake, J., Millimet, D., 2014a. An Empirical Analysis of Trade-Related Redistribution and the Political Viability of Free Trade. Available at: \url{http://people.smu.edu/jlake/pdfs/VotingFTAs.pdf}

	\item Lake, J., Millimet, D., 2014b. Revisiting the link between PAC Contributions and Lobbying Expenditures. Available at: \url{http://people.smu.edu/jlake/pdfs/PACcontributionsLobbying.pdf}

	\item Mansfield, E., Milner, H., 2012. Votes, Vetoes, and the Political Economy of International Trade Agreements. Princeton and Oxford: Princeton  University Press.

	\item Milner, H., Rosendorff, B.P., 1997. Democratic Politics and International trade Negotiations: Elections and Divided Government as Constraints on Trade Liberalization. Journal of Conflict Resolution 41, 117-147.

	\item Ornelas, E., 2005. Rent Destruction and the Political Viability of Free Trade Agreements. Quarterly Journal of Economics 120, 1475-1506.
